Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events

### 2016-06-20 Manuscript/MS- What is LDD.tex
Added Fig 4 and moved fig to Suppl Mat. Edited figure legends.

\textbf{Figure 3}. LDD events depend on a combination of disperser characteristics and landscape features. While different ***.\\

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the short- and long-distance seed dispersal events for \textit{Prunus mahaleb} according to the classification in Table 1.\\ 
\newpage

>>>>

\textbf{Figure 3}. Empirical frequency distributions of seed dispersal events as a function of dispersal distance by animal frugivores consuming \textit{Prunus mahaleb} fruits. In red, left (inset), frequencies of within-populations dispersal events inferred from direct assignment based on seed endocarp genotypes and maternal trees genotypes. Larger frame, left, contributions of four functional frugivore groups (small birds, medium- and large-sized birds, and mammals) to seed dissemination and proportional contributions (right bar) to dispersal of the inferred immigrant seeds (i.e., those not matching any maternal tree in the study population).\\

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the four combinations of \textit{Prunus mahaleb} seed dispersal events outlined in Table 1. These result from dissemination within (yellow) and outside (blue) the population geographic limits ($SDD_{loc}$, $LDD_{loc}$, respectively) and/or the genetic neigborhood area limits ($SDD_{neigh}$, $LDD_{ss}$, respectively).\\ 
\newpage
